%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{hyperref}
% \usepackage{fancyhdr}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

% \usepackage[T1]{fontenc}
\usepackage[OT4]{polski}
\usepackage[utf8]{inputenc}

% No item separation
\usepackage{enumitem}

\setlength{\textwidth}{5.1in} % Text width of the document

\newcommand{\ts}{\textsuperscript}

\pagestyle{plain}

% \pagenumbering{arabic}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\bf Dr. Jakub Ostrowski} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Wroc\l{}aw, Poland}
\moveleft.5\hoffset\centerline{\href{mailto:jakub@jakubostrowski.com}{jakub@jakubostrowski.com}}
\moveleft.5\hoffset\centerline{+48 797 386 727}
\moveleft.5\hoffset\centerline{\href{https://github.com/cespenar}{https://github.com/cespenar}}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{RESEARCH \\ INTERESTS}  

stellar evolution, stellar pulsations, asteroseismology, massive stars, subdwarf B stars

---------------------------------------------------------------------------------------------------------------

\section{EDUCATION}

{\bf Doctor of Philosophy in Astronomy}  \hfill Oct. 2011 - Sep. 2017 \\
{\sl University of Wroc\l{}aw, Wroc\l{}aw, Poland}

{\bf Master of Science in Astronomy}  \hfill Oct. 2006 - Sep. 2011 \\
{\sl University of Wroc\l{}aw, Wroc\l{}aw, Poland}

---------------------------------------------------------------------------------------------------------------

\section{RESEARCH \\ EXPERIENCE}  

{\bf Post-doctoral Researcher}  \hfill Sep. 2018 - Aug. 2022 \\
{\sl Pedagogical University of Cracow, Cracow, Poland}

{\bf Post-doctoral Researcher}  \hfill Sep. 2017 - Aug. 2018 \\
{\sl Nicolaus Copernicus Astronomical Center, Warsaw, Poland}

{\bf Ph.D. Student Researcher}  \hfill Oct. 2011 - Sep. 2017 \\
{\sl University of Wroc\l{}aw, Wroc\l{}aw, Poland}

---------------------------------------------------------------------------------------------------------------

\section{REFEREED \\ PUBLICATIONS} 

\begin{enumerate}
    \item Sanjayan, S., Baran, A. S., Nemeth, P., Kinemuchi, K., \textbf{Ostrowski, J.}, Sahoo, S. K., \textit{A variable star population in the open cluster NGC 6791 observed by the Kepler spacecraft}, 2022, accepted for publication in Acta Astronomica

    \item Silvotti, R., Nemeth, P., Telting, J. H., Baran, A. S., Ostensen, R. H., \textbf{Ostrowski, J.}, Sahoo, S. K., Prins, S., \href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.511.2201S/abstract}{\textit{Filling the gap between synchronized and non-synchronized sdBs in short-period sdBV+dM binaries with TESS: TIC 137608661, a new system with a well-defined rotational splitting}}, 2022, Monthly Notices of the Royal Astronomical Society, 511, 2201

    \item Sanjayan, S., Baran, A. S., \textbf{Ostrowski, J.}, Nemeth, P., Pelisoli, I., Ostensen, R., Kern, J. W., Reed, M. D., Sahoo, S. K., \href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.509..763S/abstract}{\textit{Pulsating subdwarf B stars in the oldest open cluster NGC 6791}}, 2022, Monthly Notices of the Royal Astronomical Society, 509, 763

    \item \textbf{Ostrowski, J.}, Baran, A. S., Sanjayan, S., Sahoo, S. K., \href{https://ui.adsabs.harvard.edu/abs/2021MNRAS.503.4646O/abstract}{\textit{Evolutionary modelling of subdwarf B stars using MESA with the predictive mixing and convective pre-mixing schemes}}, 2021, Monthly Notices of the Royal Astronomical Society, 503, 4646

    \item Baran, A. S., Sahoo, S. K., Sanjayan, S., \textbf{Ostrowski, J.}, \href{https://ui.adsabs.harvard.edu/abs/2021MNRAS.503.3828B/abstract}{\textit{A search for variable subdwarf B stars in TESS Full Frame Images - II. Variable objects in the northern ecliptic hemisphere}}, 2021, Monthly Notices of the Royal Astronomical Society, 503, 3828

    \item Baran, A. S., Ostensen, R. H., Heber, U., Irrgang, A., Sanjayan, S., Telting, J. H., Reed, M. D., \textbf{Ostrowski, J.}, \href{https://ui.adsabs.harvard.edu/abs/2021MNRAS.503.2157B/abstract}{\textit{Space observations of AA Doradus provide consistent mass determinations. New HW-Vir systems observed with TESS}}, 2021, Monthly Notices of the Royal Astronomical Society, 503, 2157

    \item Sahoo, S. K., Baran, A. S., Sanjayan, S., \textbf{Ostrowski, J.}, \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.499.5508S/abstract}{\textit{A search for variable subdwarf B stars in TESS full frame images - I. Variable objects in the southern ecliptic hemisphere}}, 2020, Monthly Notices of the Royal Astronomical Society, 499, 5508

    \item Sahoo, S. K., Baran, A. S., Heber, U., \textbf{Ostrowski, J.}, Sanjayan, S., Silvotti, R., Irrgang, A., Uzundag, M., Reed, M. D., Shoaf, K. A., Raddi, R., Vuckovic, M., Ghasemi, H., Zong, W., Bell, K. J., \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.2844S/abstract}{\textit{Mode identification in three pulsating hot subdwarfs observed with TESS satellite}}, 2020, Monthly Notices of the Royal Astronomical Society, 495, 2844

    \item Suchomska, K., Graczyk, D., Pietrzyński, G., Gieren, W., \textbf{Ostrowski, J.}, Smolec, R., Tkachenko, A., Górski, M., Karczmarek, P., Wielgórski, P., Zgirski, B., Thompson, I. B., Villanova, S., Pilecki, B., Taormina, M., Kołaczkowski, Z., Narloch, W., Soszyński, I., \href{https://ui.adsabs.harvard.edu/abs/2019A%26A...621A..93S/abstract}{\textit{Accurate stellar parameters and distance to two evolved eclipsing binary systems, OGLE-BLG-ECL-123903 and OGLE-BLG-ECL-296596, towards the Galactic bulge}}, 2019, Astronomy \& Astrophysics, 621, A93

    \item Graczyk, G., Pietrzy\'{n}ski, G., Thompson, I. B., Gieren, W., Pilecki, B., Konorski, P., Villanova, S., G\'{o}rski, M., Suchomska, K., Karczmarek, P., Stepie\'{n}, K., Storm, J., Taormina, M., Ko\l{}aczkowski, Z., Wielg\'{o}rski, P., Narloch, W., Zgirski, B., Gallene, A., \textbf{Ostrowski, J.}, Smolec, R., Udalski, A., Soszy\'{n}ski, I., Kervella, P., Nardetto, N., \href{https://ui.adsabs.harvard.edu/abs/2018ApJ...860....1G/abstract}{\textit{The late type eclipsing binaries in the Large Magellanic Cloud: Catalogue of fundamental physical parameters}}, 2018, The Astrophysical Journal, 860, 1

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Cugier, H., \href{http://adsabs.harvard.edu/abs/2017ApJ...835..290O}{\textit{Revising  evolutionary stage of HD 163899: The effects of convective overshooting and rotation}}, 2017, The Astrophysical Journal, 835, 290

    \item Kahraman-Alicavus, F., Niemczura, E., DeCat, P., Soydugan, E., Kolaczkowski, Z., \textbf{Ostrowski, J.}, Telting, J. H., Uytterhoeven, K., Poretti, E., Rainer, M., Suarez, J. C., Mantegazza, L., Kilmartin, P., Pollard, K. R., \href{http://adsabs.harvard.edu/abs/2016MNRAS.458.2307K}{\textit{Spectroscopic Survey of Gamma Doradus Stars I. Comprehensive atmospheric parameters and abundance analysis of Gamma Doradus stars}},  2016, Monthly Notices of the Royal Astronomical Society, 458, 2307

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \href{http://adsabs.harvard.edu/abs/2015MNRAS.447.2378O}{\textit{Pulsations in B-type supergiants with masses $M < 20 M_\odot$ before and after core helium ignition}}, 2015, Monthly Notices of the Royal Astronomical Society, 447, 2378

    \item Daszynska-Daszkiewicz, J.,\textbf{ Ostrowski, J.}, Pamyatnykh, A. A., \href{http://adsabs.harvard.edu/abs/2013MNRAS.432.3153D}{\textit{Pulsational instability in B-type supergiant stars}}, 2013, Monthly Notices of the Royal Astronomical Society, 432, 3153

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Pamyatnykh, A. A., \href{http://adsabs.harvard.edu/abs/2012AN....333..946O}{\textit{Excitation of pulsation modes in B-type supergiant stars}}, 2012, Astronomical Notes, 333, 946
\end{enumerate}

---------------------------------------------------------------------------------------------------------------

\section{NON-REFEREED \\ PUBLICATIONS} 

\begin{enumerate}

    \item Guzik, J. A., Farag, E., \textbf{Ostrowski, J.}, Evans, N. R., Neilson, H., Moschou, S., Drake, J. J., \href{https://ui.adsabs.harvard.edu/abs/2021ASPC..529...79G/abstract}{\textit{Investigating Opacity Modifications and Reaction Rate Uncertainties to Resolve the Cepheid Mass Discrepancy}}, 2021, Astronomical Society of the Pacific Conference Series, 529, 79

    \item \textbf{Ostrowski, J.}, Daszy\'{n}ska-Daszkiewicz, J., Cugier, H., \href{http://adsabs.harvard.edu/abs/2017EPJWC.15206006O}{\textit{Constraints on rotation of B-type stars from the nitrogen abundance}}, 2017, EPJ Web of Conferences, 152, 06006

    \item Pigulski, A., Baran, A., Bzowski, M., Cugier, H., Czerny, B., Daszynska-Daszkiewicz, J., Dziembowski, W.,  Handler, G., Kolaczkowski, Z., Krolikowska. M., Krzesinski, J., Maciejewski, G., Michalska, G., Molenda-Zakowicz, J., Moskalik, P., Niedzielski, A., Niemczura, E., \textbf{Ostrowski, J.}, Pamyatnykh, A., Ratajczak, M., Rucinski, S., Siwak, M., Smolec, R., Szutowicz, S., Tomov, T., Wyrzykowski, L., Zola, S., Sarna, M., \href{http://adsabs.harvard.edu/abs/2017sbcs.conf...76P}{\textit{UVSat: a concept of ultraviolet/optical photometric satellite}}, 2017, Proceedings of the Polish Astronomical Society, 5, 76

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Cugier, H., \href{http://adsabs.harvard.edu/abs/2016IAUFM..29B.567O}{\textit{Determining the evolutionary stage of HD163899 on the basis of its oscillation spectrum}}, 2016, Astronomy in Focus, 11, 567

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \href{http://adsabs.harvard.edu/abs/2015IAUS..307..226O}{\textit{Pulsations of massive stars beyond TAMS: effects of mass loss, diffusion, overshooting}}, 2015, IAU Symposium, 307, 226

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \href{http://adsabs.harvard.edu/abs/2014IAUS..301..321O}{\textit{Pulsations of blue supergiants before and after helium core ignition}}, 2014, IAU Symposium, 301, 321
\end{enumerate}

---------------------------------------------------------------------------------------------------------------

\section{TALKS}

\begin{enumerate}
    \item \textbf{Ostrowski, J.}, \textit{Evolutionary modelling of sdB stars using the MESA code}, Wroc\l{}aw, Poland, University of Wroc\l{}aw, May 25, 2020, \textbf{invited talk}

    \item \textbf{Ostrowski, J.}, Baran, A. S., Sahoo, S., Sanjayan, S., \textit{Modern evolutionary modelling of sdB stars using the MESA code}, Hendaye, France, 9th Meeting on Hot Subdwarfs and Related Objects, June 23 - 28, 2019, contributed talk

    \item \textbf{Ostrowski, J.}, \textit{Evolution and pulsations of massive stars with the effects of rotation and mixing processes}, Warsaw, Poland, Nicolaus Copernicus Astronomical Center, May 17, 2017, \textbf{invited talk}

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Cugier, H., \textit{Resolving the evolutionary stage of HD 163899 on the basis of its oscillation spectrum}, Honolulu, USA, IAU XXIX General Assembly FM17, August 3 - 14, 2015, contributed talk

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewic,z J., \textit{Pulsations of B-type supergiants and prospects for their interpretation with BRITE data}, Gdansk, Poland,  Science with BRITE-Constellation: initial results, September 14 - 18, 2015, contributed talk

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \textit{Pulsations of massive stars beyond TAMS: effects of mass loss, diffusion, overshooting}, Geneva, Switzerland, IAU Symposium 307, New windows on massive stars, asteroseismology, interferometry and spectropolarimetry, June 23-27, 2014, contributed talk

    \item \textbf{Ostrowski, J.}, \textit{Pulsation properties of B-type supergiants}, Cape Town, South Africa, South African Astronomical Observatory, May 29, 2014, \textbf{invited talk}

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \textit{Pulsations of blue supergiants before and after helium core ignition}, Wroc\l{}aw, Poland, IAU Symposium 301: Precision Asteroseismology, August 19 - 23, 2013, contributed talk

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Pamyatnykh, A. A., \textit{Excitation of pulsation modes in B-type supergiant stars}, Obergurgl, Austria, The Modern Era of Helio- and Asteroseismology, May 20 - 25, 2012, contributed talk
\end{enumerate}

---------------------------------------------------------------------------------------------------------------

\section{POSTERS}

\begin{enumerate}
    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., Cugier, H., \textit{Constraints on rotation of B-type stars from the nitrogen abundance}, San Pedro de Atacama, Chile, 22nd Los Alamos Stellar Pulsation Conference Series Meeting, wide-field variability surveys: a 21st-century perspective, November 28 - December 2, 2016

    \item \textbf{Ostrowski, J.}, Daszynska-Daszkiewicz, J., \textit{Pulsations of massive stars beyond TAMS: effects of mass loss, diffusion and overshooting}, Geneva, Switzerland, IAU Symposium 307: New Windows on Massive Stars, Asteroseismology, Interferometry and Spectropolarimetry, June 23 - 27, 2014
\end{enumerate}

---------------------------------------------------------------------------------------------------------------

\section{GRANTS \& \\ AWARDS} 

{\bf Grant PRELUDIUM} \\
Awarded by National Science Centre \\
Principal investigator \hfill Mar. 2014 - Sep. 2016

{\bf Grants for young scientists} \\
Awarded by University of Wroc\l{}aw \\
Principal investigator \hfill June 2015 - Dec. 2016 \\
Principal investigator \hfill June 2014 - Dec. 2015 \\
Principal investigator \hfill June 2013 - Dec. 2014

{\bf European Social Fund Scholarship} \hfill Oct. 2013 - July 2014

{\bf Scholarship for outstanding Ph.D. students} \hfill Oct. 2015 - June 2016 \\
$~$ \hfill Oct. 2014 - June 2015 \\
$~$ \hfill Oct. 2013 - June 2014 \\
$~$ \hfill Oct. 2011 - June 2012 \\

{\bf Ph.D. Scholarship Increase} \\
For the best Ph.D. students in the department \hfill Oct. 2015 - Sep. 2016 \\
$~$ \hfill Oct. 2014 - Sep. 2015 \\
$~$ \hfill Oct. 2013 - Sep. 2014 \\
$~$ \hfill Jan. 2012 - Sep. 2012

{\bf Ph.D. Scholarship}  \hfill Oct. 2011 - June 2017

---------------------------------------------------------------------------------------------------------------

\section{TEACHING \\ EXPERIENCE}  

{\bf Teaching Assistant} \\
MESA Summer School 2019 \\
{\sl University of California, Santa Barbara} \hfill Aug. 2019

{\bf Teaching Assistant} \\
MESA Summer School 2018 \\
{\sl University of California, Santa Barbara} \hfill Aug. 2018

{\bf Teaching Assistant} \\
MESA Summer School 2016 \\
{\sl University of California, Santa Barbara} \hfill Aug. 2016

{\bf Lecturer} \\
Stellar structure and evolution at the Summer Internship \\
{\sl University of Wroc\l{}aw} \hfill July 2016

{\bf Teaching Assistant} \\
Calculus 3 \\
{\sl University of Wroc\l{}aw }\hfill Oct. 2014 - June 2015 \\
$~$ \hfill Oct. 2013 - June 2014

{\bf Lecturer} \\
Basics of the MESA code \\
{\sl University of Wroc\l{}aw} \hfill Oct. 2013 - Jan. 2014

{\bf Teaching Assistant} \\
Astronomy in geography - the basics \\
{\sl University of Wroc\l{}aw} \hfill Oct. 2012 - June 2013 \\
$~$ \hfill Oct. 2011 - June 2011

---------------------------------------------------------------------------------------------------------------

\section{PUBLIC \\ OUTREACH}  

\textbf{Public lectures:}
\begin{enumerate}[noitemsep]
    \item The origin of chemical elements \hfill Cracow, 2019
    \item The internal life of stars \hfill  Wroc\l{}aw, 2016
    \item Eta Carinae - a ticking bomb \hfill Wroc\l{}aw, 2015
    \item Gamma-ray bursts \hfill Wroc\l{}aw, 2015
    \item Solar eclipses \hfill Wroc\l{}aw, 2015
    \item Historical supernovae \hfill Wroc\l{}aw, 2014
    \item The Solar System \hfill Wroc\l{}aw, 2014
    \item The origin of chemical elements \hfill Wroc\l{}aw, 2013
    \item Chemical evolution of the Universe \hfill Wroc\l{}aw, 2013
    \item Variable stars \hfill Wroc\l{}aw, 2011
\end{enumerate}

\textbf{Classes in planetarium for schools and general audience:}
\begin{itemize}[noitemsep]
    \item University of Wroc\l{}aw, 44 hours \hfill 2012 - 2016
\end{itemize}

---------------------------------------------------------------------------------------------------------------

\section{SKILLS}

\textbf{Astrophysical tools:}
\begin{itemize}[noitemsep]
    \item MESA
    \item GYRE
\end{itemize}

\textbf{Programming languages and frameworks:}
\begin{itemize}[noitemsep]
    \item Python (Matplotlib, Numpy, Pandas, Dash, Flask)
    \item SQL
\end{itemize}

\textbf{Markup languages:}
\begin{itemize}[noitemsep]
    \item \LaTeX
    \item Markdown
\end{itemize}

---------------------------------------------------------------------------------------------------------------

\section{LANGUAGES}

\begin{itemize}[noitemsep]
    \item English - C1/Professional
    \item German - A2/B1
    \item Polish - Native
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}

% Wyra\.{z}am zgod\k{e} na przetwarzanie moich danych osobowych zawartych w moim wniosku dla potrzeb niezb\k{e}dnych do realizacji procesu rekrutacji (zgodnie z ustaw\k{a} z dnia 29 sierpnia 1997 r. o ochronie danych osobowych, tekst jednolity: Dz. U. 2016 r. poz. 922).

\end{document}